Unit tests

### 2018-03-08 Tests.Rmd
tests for ncsurrog added

plot(res[,1,1],res[,2,1],type='p',asp=1) #should look like a Gumbel
rect(0,0,1,1)
BiCopGofTest(res[,1,1],res[,2,1],family=4) #should indicate an acceptable fit
BiCopGofTest(res[,1,2],res[,2,2],family=4) #should indicate an acceptable fit
BiCopGofTest(res[,1,3],res[,2,3],family=4) #should indicate an acceptable fit

@@

Test to see whether changing the copula
markedly influences the distribution
of the spatial mean:
```{r test_copsurrog2d_spatmean, echo=T, cache=T, cache.extra=list(mtime("copsurrog2d.R"),mtime("SkewnessAnd3CentMom.R"))}
set.seed(101)

@@

>>>>

plot(res[,1,1],res[,2,1],type='p',asp=1) #should look like a Gumbel
rect(0,0,1,1)
BiCopGofTest(res[,1,1],res[,2,1],family=4) #should indicate an acceptable fit; 
                                            #family=4 is Gumbel
BiCopGofTest(res[,1,2],res[,2,2],family=4) #should indicate an acceptable fit
BiCopGofTest(res[,1,3],res[,2,3],family=4) #should indicate an acceptable fit

@@

Test copsurrog2d to see whether changing the copula
markedly influences the distribution
of the spatial mean:
```{r test_copsurrog2d_spatmean, echo=T, cache=T, cache.extra=list(mtime("copsurrog2d.R"),mtime("SkewnessAnd3CentMom.R"))}
set.seed(101)

@@

Test the ncsurrog function:
```{r test_ncsurrog, echo=T, cache=T, cache.extra=list(mtime("ncsurrog.R"))}
source("ncsurrog.R")
set.seed(103)

#test without NAs
cop<-claytonCopula(5,3)
numpts<-1000
m<-rCopula(numpts,cop)
plot(m[,1],m[,2],type='p',asp=1)
rect(0,0,1,1)
plot(m[,1],m[,3],type='p',asp=1)
rect(0,0,1,1)
res<-ncsurrog(m,"kendall",3)
if (sum(dim(res)==c(1000,3,3))==3)
{
  print("passed")
} else
{
  print("dimension wrong in ncsurrog output")
}

plot(res[,1,1],res[,2,1],type='p',asp=1)
rect(0,0,1,1) #should look like a normal copula
plot(res[,1,1],res[,3,1],type='p',asp=1)
rect(0,0,1,1) #should look like a normal copula

#these should show an adequate fit
ncop<-normalCopula(.5,2)
BiCopGofTest(res[,1,1],res[,2,1],family=1)
BiCopGofTest(res[,1,2],res[,2,2],family=1)
BiCopGofTest(res[,1,3],res[,2,3],family=1)

#test with NAs
m[sample(1:numpts,5),1]<-NA
m[sample(1:numpts,5),2]<-NA
m[sample(1:numpts,5),3]<-NA
res<-ncsurrog(m,"kendall",3)
if (sum(dim(res)==c(1000,3,3))==3)
{
  print("passed")
} else
{
  print("dimension wrong in ncsurrog output")
}

sum(is.na(res[,1,1])) #these should all be 5
sum(is.na(res[,2,1]))
sum(is.na(res[,1,2]))
sum(is.na(res[,2,2]))

plot(res[,1,1],res[,2,1],type='p',asp=1)
rect(0,0,1,1) #should look like a normal copula
plot(res[,1,1],res[,3,1],type='p',asp=1)
rect(0,0,1,1) #should look like a normal copula

#these should show an adequate fit
BiCopGofTest(res[,1,1],res[,2,1],family=1)
BiCopGofTest(res[,1,2],res[,2,2],family=1)
BiCopGofTest(res[,1,3],res[,2,3],family=1)
```
